D_exp_2

### 2018-08-12 experiments/C_exp_1/writeup/C_exp_1.Rmd
consistent C, D, and E formats in RMD

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Number, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Number) %>%
    spread(key=Vagueness, value=Instruction)
# kable(instructions_table, format="latex", booktabs = TRUE)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

@@

```{r, echo=F}
dat_plot <- summarySEwithin2(dat, measurevar="RT_log", withinvars=c("Vagueness", "Number", "Item"), idvar="Subject")
```

```{r, "RT condition means plot", fig.width=7, fig.height=3.5, echo=FALSE, results='hide'}
# correction from Morey (2008) applied to condition means
mywidth=0
pdodge=position_dodge(width=mywidth)
#
ggplot(dat_plot, aes(x=Item, y=RT_logNormed, group=Vagueness, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci, shape=Vagueness, fill=Vagueness)) +
  ggtitle("Response time condition means") +
  facet_wrap(~Number) +
  scale_fill_grey(name="Vagueness", start=0, end=1) +
  scale_shape_manual(name="Vagueness", values=c(21,22)) +
  theme(aspect.ratio = 1, panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(fill="white", colour="black"), strip.background=element_blank(), legend.key = element_blank(), legend.key.size=unit(4, 'mm'), legend.position="top", axis.text.x = element_text(angle = 15)) +
  ylab("RT log(ms)") + xlab(NULL) +
  #
  geom_errorbar(position=pdodge, width=0.25) +
  geom_line(position=pdodge) +
  geom_point(position=pdodge, size=2)

```{r, "Borderline response distribution plot", fig.width=7, fig.height=3.5, echo=FALSE, results='hide'}
dat_borderline$response_category <- relevel(dat_borderline$response_category, ref='expected')

@@

Original full model
```{r "original full RT model", echo=F, cache=TRUE}
dat_model <- dat
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Num <- ifelse(dat_model$Number=="Verbal", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtFullModel <- lmerTest::lmer(1 + RT_log ~ c_Vag * c_Num + c_Itm + (1 + c_Vag * c_Num + c_Itm | Subject), dat_model)
pretty_coef_table(rtFullModel, "rtFullModel")
```

Numeric only
```{r, echo=FALSE}
dat_model <- droplevels(subset(dat, Number=="Numeric"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtFullModel_num <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject), dat_model)
pretty_coef_table(rtFullModel_num, "rtFullModel_num")
```

Verbal only
```{r, echo=FALSE}
dat_model <- droplevels(subset(dat, Number=="Verbal"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtFullModel_verb <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject), dat_model)
pretty_coef_table(rtFullModel_verb, "rtFullModel_verb")
```

Borderline model
```{r 'bl-full-model', cache=TRUE, echo=FALSE}
dat_model <- dat_borderline
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Num <- ifelse(dat_model$Number=="Verbal", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
blFullModel <- lme4::glmer(isBorderline ~ c_Vag * c_Num + c_Itm + (1 + c_Vag * c_Num + c_Itm | Subject), dat_model, family="binomial", control = glmerControl(optimizer = "bobyqa"))
pretty_coef_table(blFullModel, "blFullModel")
```

@@

Model of the data after the 6:15:24 level of Item is removed
```{r, echo=F, cache=TRUE}
dat_model <- droplevels(subset(dat, Item!="06:15:24"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Num <- ifelse(dat_model$Number=="Verbal", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="16:25:34", -.3333, ifelse(dat_model$Item=="26:35:44", .0000, .3333))
rtRestrictedModel <- lmerTest::lmer(1 + RT_log ~ c_Vag * c_Num + c_Itm + (1 + c_Vag + c_Num  | Subject), dat_model)
pretty_coef_table(rtRestrictedModel, "rtRestrictedModel")
```

Numeric only after the 6:15:24 level of Item is removed
```{r, echo=F, cache=TRUE}
dat_model <- droplevels(subset(dat, Item!="06:15:24" & Number=="Numeric"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="16:25:34", -.3333, ifelse(dat_model$Item=="26:35:44", .0000, .3333))
rtRestrictedModel_num <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag | Subject), dat_model)
pretty_coef_table(rtRestrictedModel_num, "rtRestrictedModel_num")
```

Verbal-only after the 6:15:24 level of Item is removed
```{r, echo=F, cache=TRUE}
dat_model <- droplevels(subset(dat, Item!="06:15:24" & Number=="Verbal"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="16:25:34", -.3333, ifelse(dat_model$Item=="26:35:44", .0000, .3333))
rtRestrictedModel_verb <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject), dat_model)
pretty_coef_table(rtRestrictedModel_verb, "rtRestrictedModel_verb")
```

>>>>

```{r, "full table of instructions", echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Number, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Number) %>%
    spread(key=Vagueness, value=Instruction)
# kable(instructions_table, format="latex", booktabs = TRUE)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

@@

```{r, "make summary data for rt plot", echo=FALSE}
dat_plot <- summarySEwithin2(dat, measurevar="RT_log", withinvars=c("Vagueness", "Number", "Item"), idvar="Subject")
```

```{r, "EXP_C_RT_condition_means_plot", fig.width=7, fig.height=3.5, echo=FALSE}
mywidth=0
pdodge=position_dodge(width=mywidth)
ggplot(dat_plot, aes(x=Item, y=RT_logNormed, group=Vagueness, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci, shape=Vagueness, fill=Vagueness)) +
  ggtitle("Response time condition means") +
  facet_wrap(~Number) +
  scale_fill_grey(name="Vagueness", start=0, end=1) +
  scale_shape_manual(name="Vagueness", values=c(21,22)) +
  theme(aspect.ratio = 1, panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_rect(fill="white", colour="black"), strip.background=element_blank(), legend.key = element_blank(), legend.key.size=unit(4, 'mm'), legend.position="top", axis.text.x = element_text(angle = 15)) +
  ylab("RT log(ms)") + xlab(NULL) +
  geom_errorbar(position=pdodge, width=0.25) +
  geom_line(position=pdodge) +
  geom_point(position=pdodge, size=2)
```

```{r, "EXP_C_Borderline_response_distribution_plot", fig.width=7, fig.height=3.5, echo=FALSE}
dat_borderline$response_category <- relevel(dat_borderline$response_category, ref='expected')

@@

Original full model
```{r "original full RT model", cache=TRUE}
dat_model <- dat
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Num <- ifelse(dat_model$Number=="Verbal", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtFullModel <- lmerTest::lmer(1 + RT_log ~ c_Vag * c_Num + c_Itm + (1 + c_Vag * c_Num + c_Itm | Subject), dat_model)
pretty_coef_table(rtFullModel, "rtFullModel")
```

Numeric only
```{r "numeric only RT model", cache=TRUE}
dat_model <- droplevels(subset(dat, Number=="Numeric"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtFullModel_num <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject), dat_model)
pretty_coef_table(rtFullModel_num, "rtFullModel_num")
```

Verbal only
```{r "verbal only RT model", cache=TRUE}
dat_model <- droplevels(subset(dat, Number=="Verbal"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtFullModel_verb <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject), dat_model)
pretty_coef_table(rtFullModel_verb, "rtFullModel_verb")
```

Borderline model
```{r "borderline full model", cache=TRUE}
dat_model <- dat_borderline
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Num <- ifelse(dat_model$Number=="Verbal", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
blFullModel <- lme4::glmer(isBorderline ~ c_Vag * c_Num + c_Itm + (1 + c_Vag * c_Num + c_Itm | Subject), dat_model, family="binomial", control = glmerControl(optimizer = "bobyqa"))
pretty_coef_table(blFullModel, "blFullModel")
```

@@

Model of the data after the 6:15:24 level of Item is removed
```{r, "full RT model after drop item", cache=TRUE}
dat_model <- droplevels(subset(dat, Item!="06:15:24"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Num <- ifelse(dat_model$Number=="Verbal", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="16:25:34", -.3333, ifelse(dat_model$Item=="26:35:44", .0000, .3333))
rtRestrictedModel <- lmerTest::lmer(1 + RT_log ~ c_Vag * c_Num + c_Itm + (1 + c_Vag + c_Num  | Subject), dat_model)
pretty_coef_table(rtRestrictedModel, "rtRestrictedModel")
```

Numeric only after the 6:15:24 level of Item is removed
```{r, "num only RT model after drop item", cache=TRUE}
dat_model <- droplevels(subset(dat, Item!="06:15:24" & Number=="Numeric"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="16:25:34", -.3333, ifelse(dat_model$Item=="26:35:44", .0000, .3333))
rtRestrictedModel_num <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag | Subject), dat_model)
pretty_coef_table(rtRestrictedModel_num, "rtRestrictedModel_num")
```

Verbal-only after the 6:15:24 level of Item is removed
```{r, "verbal only RT model after drop item", cache=TRUE}
dat_model <- droplevels(subset(dat, Item!="06:15:24" & Number=="Verbal"))
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="16:25:34", -.3333, ifelse(dat_model$Item=="26:35:44", .0000, .3333))
rtRestrictedModel_verb <- lmerTest::lmer(1 + RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject), dat_model)
pretty_coef_table(rtRestrictedModel_verb, "rtRestrictedModel_verb")
```

### 2018-08-12 experiments/D_exp_2/writeup/D_exp_2.Rmd
consistent C, D, and E formats in RMD

```{r}
dat <- preprocessing(root_dir, data_dir)
dat <- perSubjectTrim.fnc(dat, response='RT', subject='Subject', trim = 2.5)$data
dat$RT_log <- log(dat$RT)
```

@@

```{r trimat25sd}
dat_plot <- summarySEwithin2(dat, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r rtplot1, fig.width=7, fig.height=3}
dodge = position_dodge(width=0.2)
dat_plot$Condition <- as.factor(paste(sep=' ', dat_plot$Selection, dat_plot$Vagueness))
rtplot=ggplot(dat_plot,
              aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
rtplot
```

```{r}
dat_borderline <- dat
```

```{r, "Borderline response distribution plot", fig.width=7, fig.height=3.5, echo=FALSE, results='hide'}
dat_borderline$response_cat <- factor(dat_borderline$response_cat, levels= c("Near", "Expected", "Far"))

ggplot(dat_borderline) + 
  geom_bar(aes(response_cat, group=Selection:Vagueness, fill=Vagueness), position=position_dodge(width=NULL)) +   
  scale_fill_grey() + 
  xlab(NULL) + 
  ggtitle('Borderline response distribution') + 
  facet_grid(~Selection) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank(), legend.position="top", aspect.ratio=1, plot.background = element_rect(fill=NA, color='white'), strip.background=element_blank(), legend.key.size=unit(4, 'mm'), axis.text.x = element_text(angle = 15))

```

@@

```{r rtlmer, cache=TRUE, results='asis'}
dat_model <- dat
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtlmer = lmerTest::lmer(data=dat_model,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
pretty_coef_table(rtlmer, "rtlmer")
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-5}
dat_model <- subset(dat, subset=Selection=='Comparison')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s1lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s1lm, "s1lm")
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-5}
dat_model <- subset(dat, subset=Selection=='Matching')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s2lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s2lm, "s2lm")
```

>>>>

```{r}
dat_full <- preprocessing(root_dir, data_dir)
dat <- subset(dat_full, subset=RT>0 & RT<49871)
dat_borderline <- dat
dat <- perSubjectTrim.fnc(dat, response='RT', subject='Subject', trim = 2.5)$data
dat$RT_log <- log(dat$RT)
```

@@

```{r}
dat_plot <- summarySEwithin2(dat, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r, "EXP_D_RT_means_plot", fig.width=7, fig.height=3, echo=FALSE}
dodge = position_dodge(width=0.2)
dat_plot$Condition <- as.factor(paste(sep=' ', dat_plot$Selection, dat_plot$Vagueness))
ggplot(dat_plot, aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci, group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
```

```{r, "EXP_D_Borderline_response_distribution_plot", fig.width=7, fig.height=3.5, echo=FALSE}
dat_borderline$response_cat <- factor(dat_borderline$response_cat, levels= c("Near", "Expected", "Far"))
ggplot(dat_borderline) + 
  geom_bar(aes(response_cat, group=Selection:Vagueness, fill=Vagueness), position=position_dodge(width=NULL)) +   
  scale_fill_grey() + 
  xlab(NULL) + 
  ggtitle('Borderline response distribution') + 
  facet_grid(~Selection) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank(), legend.position="top", aspect.ratio=1, plot.background = element_rect(fill=NA, color='white'), strip.background=element_blank(), legend.key.size=unit(4, 'mm'), axis.text.x = element_text(angle = 15))
```

@@

```{r, "rt_lmer_full_model_all_items", cache=TRUE}
dat_model <- dat
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtlmer = lmerTest::lmer(data=dat_model, RT_log ~ c_Vag * c_Sel + c_Itm + (1 + c_Vag * c_Sel + c_Itm | Subject))
pretty_coef_table(rtlmer, "rt_lmer_full_model_all_items")
```

```{r, "rt_lmer_for_comparison_all_items", cache=TRUE}
dat_model <- subset(dat, subset=Selection=='Comparison')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
comp_lmer <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(comp_lmer, "rt_lmer_for_comparison_all_items")
```

```{r, "rt_lmer_for_matching_all_items", cache=TRUE}
dat_model <- subset(dat, subset=Selection=='Matching')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
match_lmer <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(match_lmer, "rt_lmer_for_matching_all_items")
```
